Multi-level modeling with Openflexo/\FML

### 2022-03-09 5-analysis.tex

In a first step, the federation approach is mainly based on modeling relationships between several models, independently of their abstraction level and the model architecture.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9 \columnwidth]{Figures/MultilevelArchitecture.pdf}
    \caption{Multilevel architecture of our solution}
    \label{fig:MultilevelArchitecture}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0 \columnwidth]{Figures/Instantiation.pdf}
    \caption{Problem  domain linguistic and ontologic instantiation}
    \label{fig:LinguisticAndOntologicInstantiation}
\end{figure}

Based on this approach, we organize our set of models following the
architecture of the aforementioned Fig.~\ref{fig:MultilevelArchitecture}. The
resulting multi-level architecture is organized in two virtual models, one
defining the core concepts metamodel including the definition of Processes and
Tasks, and one, the Acme metamodel, extending the previous model to specialize
the Acme definitions. The \FML language defines multiple inheritance concept
between virtual models as illustrated in the Sect.~\ref{sec:AcmeSoftwareDevelopmentProcess}.

Finally, as explained previously, the defined level for the Acme  and the XSure models is the result of the instantiation of virtual models. In our approach this virtual model instance level can not be specialized or extended but all the other virtual models could be extended by any concepts, as a new federated model.
Also, the instance level can be instantiated from any virtual model, which represents any metamodel level.

>>>>

In a first step, the federation approach is mainly based on modeling relationships between several models, independent of their abstraction levels and the modeling architecture.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9 \columnwidth]{Figures/MultilevelArchitecture-1.5.pdf}
    \caption{Multilevel architecture of our solution}
    \label{fig:MultilevelArchitecture}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0 \columnwidth]{Figures/Instantiation-1.5.pdf}
    \caption{Problem  domain linguistic and ontologic instantiation}
    \label{fig:LinguisticAndOntologicInstantiation}
\end{figure}

{\color{red} I do not know what is the legend of figure 5.  However, if all four modeled concepts are virtual models, their graphical representation should be the same. I find the same problem with figure 3. As a matter of fact all models from Figure 2, 3 and 5 use various representations and one wonders when it is UML, when it is a conceptual model?}Based on this approach, we organize our set of models following the
architecture of the aforementioned Fig.~\ref{fig:MultilevelArchitecture}. The
resulting multi-level architecture is organized in two virtual models, one
defining the core concepts metamodel including the definition of Processes and
Tasks, and one, the Acme metamodel, extending the previous model to specialize
the Acme definitions. The \FML language defines multiple inheritance concept
between virtual models as illustrated in the Sect.~\ref{sec:AcmeSoftwareDevelopmentProcess}.

Finally, as explained previously, the defined level for the Acme  and the XSure models is the result of the instantiation of virtual models. In our approach this virtual model instance level can not be specialized or extended but all the other virtual models could be extended by any concepts, as a new federated model.
Furthermore, the instance level can be instantiated from any virtual model, which represents any metamodel level.
